---
title: "TP_Decision_Theory"
author: "Arnaud Frering"
date: "20/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
```

```{r,}
library('GA')
```

#1
## 1.1

The database has 8 attributes :

1. Sequence Name: Accession number for the SWISS-PROT database
2. mcg: McGeoch's method for signal sequence recognition.
3. gvh: von Heijne's method for signal sequence recognition.
4. lip: von Heijne's Signal Peptidase II consensus sequence score. Binary attribute.
5. chg: Presence of charge on N-terminus of predicted lipoproteins. Binary attribute.
6. aac: score of discriminant analysis of the amino acid content of outer membrane and periplasmic proteins.
7. alm1: score of the ALOM membrane spanning region prediction program.
8. alm2: score of ALOM program after excluding putative cleavable signal regions from the sequence.

The class is the localisation site which can be :

1. cp: cytoplasm
2. im: inner membrane without signal sequence
3. imS: inner membrane, cleavable signal sequence
4. imL: inner membrane lipoprotein
5. imU: inner membrane, uncleavable signal sequence
6. om: outer membrane
7. omL: outer membrane lipoprotein
8. pp: periplasm


## 1.2

```{r}
data_ecoli = read.table("ecoli.data",header = FALSE, sep = "")
names(data_ecoli) = c('Sequence Name', 'mcg', 'gvh', 'lip', 'chg', 'aac', 'alm1', 'alm2', 'Class')
```

```{r}
print(data_ecoli)
```

```{r}

```

#2
##2.1

```{r}
library('class')

kdist <- knn.dist(df_train)
preds <- knn.pred(df_train,df_test,y, kdist,k=10, agg.meth="majority")
preds

```

##2.2

```{r}
library('evclass')

EkNN <- EkNNfit(x = x_train, y = y_train, K = 10,)
preds <- EkNNval(xtrain, ytrain, xtest, K = 10, ytest = NULL)


```