---
title: "TP_belief"
author: "seb"
date: "20/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("GA")
library("class")
library("evclass")
```

Q 1.1)

The database has 8 attributes :

1. Sequence Name: Accession number for the SWISS-PROT database
2. mcg: McGeoch's method for signal sequence recognition.
3. gvh: von Heijne's method for signal sequence recognition.
4. lip: von Heijne's Signal Peptidase II consensus sequence score. Binary attribute.
5. chg: Presence of charge on N-terminus of predicted lipoproteins. Binary attribute.
6. aac: score of discriminant analysis of the amino acid content of outer membrane and periplasmic proteins.
7. alm1: score of the ALOM membrane spanning region prediction program.
8. alm2: score of ALOM program after excluding putative cleavable signal regions from the sequence.

The class is the localisation site which can be :

1. cp: cytoplasm
2. im: inner membrane without signal sequence
3. imS: inner membrane, cleavable signal sequence
4. imL: inner membrane lipoprotein
5. imU: inner membrane, uncleavable signal sequence
6. om: outer membrane
7. omL: outer membrane lipoprotein
8. pp: periplasm

Q 1.2)
```{r}

data_ecoli = read.table("ecoli.data",header = FALSE, sep = "")
names(data_ecoli) = c('Sequence Name', 'mcg', 'gvh', 'lip', 'chg', 'aac', 'alm1', 'alm2', 'Class')

class <- as.data.frame(table(data_ecoli$Class))
data_ecoli <- data_ecoli[data_ecoli$Class %in% class$Var1[class$Freq>=6],]

data_ecoli <- droplevels(data_ecoli)

index_train <- rep(c(T,F), length.out=327)
train_data <- data_ecoli[which(index_train), 2:8]
test_data <- data_ecoli[which(!index_train),2:8]
train_labels <- data_ecoli[which(index_train), 9]
test_labels <- data_ecoli[which(!index_train), 9]
```

Q 2.1)
```{r}
Ypred <- knn(train_data, test_data, cl=train_labels, k=10)

conf_matrix <- table(Ypred, test_labels)

accuracy <- function(confusion_matrix){sum(diag(confusion_matrix)/(sum(rowSums(confusion_matrix)))) * 100}
acc_knn <- accuracy(conf_matrix)
```

Q 2.2)
```{r}


train_labels_matrix <- as.matrix(train_labels)
test_labels_matrix <- as.matrix(test_labels)
fit <- EkNNfit(train_data, train_labels_matrix, K=10)
EvYpred <- EkNNval(train_data, train_labels_matrix, test_data, 10, test_labels_matrix, fit$param)
M1 <- EvYpred$m
```

Q 2.4)
```{r}
conf_matrix <- table(EvYpred$ypred, test_labels)
acc_Eknn <- accuracy(conf_matrix)
print(paste("knn accuracy : ", acc_knn, "%"))
print(paste("Evidential knn accuracy : ", acc_Eknn,"%"))
```

Q 2.5)
```{r}
load("M2")
```

Q 3.1)
```{r}
#Definition de la loss function avec beta = 1
Loss<-function(A, theta, beta){
  resultat = 1
  elements_A = sum(decimal2binary(A))
  if (binary2decimal(decimal2binary(theta,5) & decimal2binary(A,5)) != 0){
    resultat = 1 - ((1 + beta^2) / (beta^2 + elements_A))
  }
  resultat #la fonction retourne le résultat
}
```

```{r}
# Initialisation de la matrice de loss
nb_classes = 5
nb_sous_ensembles = 2^nb_classes -1
LOSS <- matrix(rep(c(0), nb_classes * nb_sous_ensembles), nb_sous_ensembles, nb_classes)
for (i in 1:nb_classes){
  for (j in 1:nb_sous_ensembles){
    LOSS[j, i] = Loss(A = j, theta = i, beta = 1)
  }
}
```

```{r}
library(plot.matrix)
plot(LOSS)
```

Q 3.2)
```{r}
risk <- function(A, m){
  res <- 0
  for(b in 1:nrow(LOSS)){
    mass <- m[b]
    loss_list <- c(0)
    for(theta in 1:5){
      if(binary2decimal(decimal2binary(theta, length = 5) & decimal2binary(b, length =5)) != 0){
        loss_list <- c(loss_list, LOSS[A,theta])
      }
    }
    max_loss <- max(loss_list)
    res <- res + (mass * max_loss)
  }
  res
}

get_prediction <- function(m){
  cautious_prediction <- c()
  for(a in 1:nrow(LOSS)){
    cautious_prediction <- c(cautious_prediction, risk(a, m))
  }
  return(unname(which.min(cautious_prediction)))
}

compute_predictions <- function(M){
  predictions <- c()
  for(i in 1:nrow(M)){
    pred <- get_prediction(M[i, ])
    predictions <- c(predictions, pred)
  }
  predictions
}

cautious_predictions <- compute_predictions(M2)
nb_predictions <- as.data.frame(table(cautious_predictions))

# number of prediction per subset
subset_pred <- nb_predictions[nb_predictions$cautious_predictions != 1 & nb_predictions$cautious_predictions != 2 & nb_predictions$cautious_predictions != 4 & nb_predictions$cautious_predictions != 8 & nb_predictions$cautious_predictions != 16, ]
subset_pred

# total number of subsets cautious predictions
print("total number of subsets cautious predictions :")
sum(subset_pred$Freq)
```



